---
title: "Challenge-6"
author: "CHEN JUNYU RYAN"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Countdown Blastoff (While Loop)

Create a program that simulates a rocket launch countdown using a while loop. Start from 10 and countdown to "Blastoff!" with a one-second delay between each countdown number. Print a message when the rocket launches.

**Hint:** You may want to use `cat` command to print the countdown and `Sys.sleep` for incorporating the delay

**Output preview:** Here is how the countdown could look like 

**Solutions:**

```{r, eval=T,echo=TRUE}
countdown <- 10

while (countdown >= 1) {
  cat(countdown, "\n")
  Sys.sleep(1)  # Pause for 1 second
  countdown <- countdown - 1
}

cat("Blastoff!\n")





```
<br>

#### Question-2: Word Reverser (for Loop)

Develop a program that takes a user-entered word and uses a while loop to print the word's characters in reverse order. For example, if the user enters "hello," the program should print "olleh."

**Hint:** You may want to use `substr` command to access each character of the input word, and `paste` command to join the reversed letters one at a time

**Solutions:** 

```{r, eval=T,echo=TRUE}
# Get user input
word <- readline(prompt = "Enter a word: ")

# Initialize variables
length_word <- nchar(word)
reverse_word <- ""
index <- length_word

# Use a while loop to reverse the word
while (index > 0) {
  reverse_word <- paste(reverse_word, substr(word, index, index), sep = "")
  index <- index - 1
}

# Print the reversed word
cat("Reversed word:", reverse_word, "\n")





```
<br>
